Effects of sexual selection on non-sexual fitness components: a meta-analysis

### 2018-05-18 meta_analysis_sexual_selection_pop_fitness.Rmd
Bayesian update

```{r, warning=FALSE, message=FALSE, results='hide'}
library(pander)
library(tidyr)
library(compute.es)
library(metafor)
library(plyr)
library(dplyr)
library(lme4)
library(forestplot)
library(ggplot2)
library(ggthemes)
library(kableExtra)
library(ggrepel)
library(reshape2)
library(RColorBrewer)
source("Vdodge_function.R") # nice function for ggplot
```

@@

```{r}
anova(model.complete2, L=c(1, 0, 0, -1, 0, 0)) 
```

>>>>

```{r, warning=FALSE, message=FALSE, results='hide'}
library(pander)
library(tidyr)
library(compute.es)
library(metafor)
library(plyr)
library(dplyr)
library(lme4)
library(forestplot)
library(ggplot2)
library(ggthemes)
library(kableExtra)
library(ggrepel)
library(reshape2)
library(RColorBrewer)
library(ggridges)
source("Vdodge_function.R") # nice function for ggplot
```

@@

```{r}
anova(model.complete2, L=c(1, 0, 0, -1, 0, 0)) 
```
__________________________________

###Bayesian models using _brms_ package

We can run a bayesian model using the brms package. The model has the same moderators as the REML approach used above. 
```{r, warning=FALSE}
library(rstan) #Note that installation requires some effort
library(brms) 
library(backports) #seems to be a dependency
```

```{r, warning = FALSE, results='hide', message=FALSE}
#Use brm to create a model similar to the one used in the REML approach. 
#Use brm to create a model similar to the one used in the REML approach. 
meta.brms <- brm(g| se(sqrt(var.g), sigma = TRUE)  ~ 1 + Sex * Environment #response is Hedges' g and the standard error associated with it (sqrt(var.g)) with sex and environment as moderators
                + (1|Study.ID) #group level effect #1
                + (1|Outcome), #group level effect #2 (unrelated/crossed) with #1
                family = "gaussian", #default
                seed = 1,
                cores = 4, chains = 4, iter = 4000, #Run 4 chains in parrallel for 4000 iterations (2000 are burn in)
                control = list(adapt_delta = 0.99),
                data = restricted.data)
```

```{r}
summary(meta.brms)
```

Plot summary of the model estimates
```{r}
plot(meta.brms)
```

We can also obtain marginal effects plots

> Are these like the predictions?

```{r}
marginaleffects <- marginal_effects(meta.brms)
```

Obtain fitted values: **Note that the fitted values obtained here have much smaller error than the predict values, which blow out**

```{r}
#obtain average variance of each group in the prediction
av.var.g <- as.numeric(c(restricted.data %>% filter (Sex == 'M' & Environment == "Unstressed") %>% summarise(mean = mean(var.g)),
              restricted.data %>% filter (Sex == 'B' & Environment == "Unstressed") %>% summarise(mean = mean(var.g)),
              restricted.data %>% filter (Sex == 'F' & Environment == "Unstressed") %>% summarise(mean = mean(var.g)),
              restricted.data %>% filter (Sex == 'M' & Environment == "Stressed") %>% summarise(mean = mean(var.g)),
              restricted.data %>% filter (Sex == 'B' & Environment == "Stressed") %>% summarise(mean = mean(var.g)),
              restricted.data %>% filter (Sex == 'F' & Environment == "Stressed") %>% summarise(mean = mean(var.g))))

#Expand grid for environment and sex
brms.newdata <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
                           Environment = c("Unstressed", "Stressed")))
#Add variance
brms.newdata$var.g <- av.var.g

#Add predictions
brms.predict <- fitted(meta.brms, newdata = brms.newdata, re_formula = NA)
brms.predict <- as.data.frame(brms.predict)
brms.predictions <- data.frame(brms.newdata$Sex, brms.newdata$Environment, brms.predict$Estimate, brms.predict$Est.Error, brms.predict$Q2.5, brms.predict$Q97.5)

#Add sample size 
brms.predictions$n <- as.numeric(predictions.complete2$n)

#Name columns
colnames(brms.predictions) <- c("Sex", "Environment", "Estimate", "Error", "LCI", "UCI", "n")
```

Plot results for brms prediction using the same ggplot code as for the metafor model predictions

```{r, fig.height=6, fig.width = 6}
EnvSex.metaanalysis.brms <- brms.predictions %>% 
      mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female")) %>%
  ggplot(aes(x = Estimate, y= Environment, fill = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
  geom_errorbarh(aes(xmin = brms.predictions$LCI, 
                     xmax = brms.predictions$UCI,
                     color = Sex), height = 0, position = pd, show.legend = F) +
  geom_point(aes(size=n), position = pd, shape=21, color = "grey20") + 
  scale_size(guide = 'none')+
  ylab("Environment\n")+
  xlab("\nEffect Size (Hedges' g)")+
  scale_fill_brewer(palette = "Set1")+
  scale_color_brewer(palette = "Set1")+
  guides(fill = guide_legend(reverse=T, override.aes = list(size = 3)))+
  scale_x_continuous(limits = c(-0.2, 1), breaks = c(-0.2, 0, 0.2, 0.4, 0.6, 0.8, 1))+

EnvSex.metaanalysis.brms
```
<br></br>
**Figure X** Bayesian fitted values for effect size using a comprable model to the one used in the REML approach

Let's get the distribution of posterior fitted values and plot with ggridges

```{r}
#Obtain posterior fitted values and transform
posterior_fit <- data.frame(t(posterior_linpred(meta.brms, newdata = brms.newdata, re_formula = NA)))

#Add columns for Environment and Sex
posterior_fit$Sex <- c("Male", "Both", "Female", "Male", "Both", "Female")
posterior_fit$Environment <- c("Benign_Male", "Benign_Both", "Benign_Female", "Stressful_Male", "Stressful_Both", "Stressful_Female")

#Clean up dataframe
posterior_fit <- melt(posterior_fit, id = c("Sex", "Environment"))
posterior_fit$variable <- NULL
```

```{r, fig.height=8, fig.width=8}
posterior_fit %>% ggplot(aes(x=value, y = Environment, fill = Sex))+
  geom_density_ridges2(alpha = 0.75)+
  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
    ylab("Environment\n")+
  xlab("\nPosterior Effect Size (Hedges' g)")+
  scale_fill_brewer(palette = "Set1")+
  scale_color_brewer(palette = "Set1")+
  guides(fill = guide_legend(reverse=T, override.aes = list(size = 0.5)))+
  scale_x_continuous(limits = c(-0.5, 1.2), breaks = c(-1, -.5, 0, 0.5, 1))+

  theme(panel.spacing = unit(0.5, "lines"),
        text = element_text(size=14),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.text = element_text(size=14), 
        legend.title=element_text(size=14, 
                                  face = "bold"),
        axis.title.x = element_text(hjust = 0.5, size = 14),
        axis.title.y = element_text(size = 14),
        axis.text.y = element_text(angle = 0),
        plot.title = element_text(size = 14))

```
<br></br>
**Figure X** Posterior fitted values for Hedges' g using the same model as above
